### 2023-12-18 documentation/thesis/thesis_document.tex
more thesis

@@

\emph{anbei werden drei erschienee sensoren für unterschiedliche
anwedungfälle } tablle statisch dynamisch

@@

\begin{itemize}
\tightlist
\item
  einfachster aufbau rp pico + sensor
\end{itemize}

\hypertarget{d-dual-sensor}{%
\subsection{1D: Dual Sensor}\label{d-dual-sensor}}

\begin{itemize}
\tightlist
\item
  gleicher abstand zwei gleicher sensoren
\item
  schnelle erkennung der plarisationsebene ggf offset vom mittelpunkt
  dieser
\end{itemize}

\hypertarget{full-sphere}{%
\subsection{Full-Sphere}\label{full-sphere}}

@@

\begin{itemize}
\tightlist
\item
  komplexester aufbau sensor + mechanik
\item
  polar mechanisches system
\item
  full sphere sensor
\end{itemize}

\hypertarget{integration-of-an-professional-teslameter}{%
\subsection{Integration of an Professional
Teslameter}\label{integration-of-an-professional-teslameter}}

\begin{itemize}
\tightlist
\item
  einfach anbindung professioneller teslameter
\item
  Voltkraft
\end{itemize}

@@

At the current state of implementation, it is only possible to detect
and use sensors that are directly connected to the \gls{pc} with the
\gls{mrp}-library. This has the disadvantage that there must always be a
physical connection. This can make it difficult to install multiple
sensors in measurement setups where space or cable routing options are
limited. To make sensors connected to a small
\passthrough{\lstinline!remote!} \gls{pc} available on the network, the
\passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
been developed. This can be a single board computer (e.g.~a Raspberry
Pi). The small footprint and low power consumption make it a good
choice. It can also be used in a temperature chamber. The approach of
implementing this via a \gls{rest} interface also offers the advantage
that several measurements or experiments can be recorded at the same
time with the sensors.

@@

If time-critical synchronisation is required, \gls{ptp} and \gls{pps}
output functionality can be used on many single-board computers, such as
the RaspberryPi Compute Module.

>>>>

\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support}, label=lst:CustomSensorClass]
#ifndef __CustomSensor_h__
#define __CustomSensor_h__
// register your custom sensor in implemented_sensors.h also
class CustomSensor: public baseSensor {}
{
public:
    CustomSensor();
    ~CustomSensor();
    // implement depending sensor communication interface
    bool begin(TwoWire& _wire_instance); // I2C
    bool begin(HardwareSerial& _serial_instance); // UART
    bool begin(Pin& _pin_instance); // ANALOG like analog input / DIGITAL PIN like onewire
    // FUNCTIONS USED BY READOUT LOGIC
    bool is_valid() override;
    String capabilities() override;
    String get_sensor_name() override;
    bool query_sensor() override;
    sensor_result get_result() override;        
};
#endif
\end{lstlisting}

@@

Two functional sensor
platforms\ref{Build_sensors_with_different_capabilities.csv} were built
in order to create a solid test platform for later tests and for the
development of the \gls{mrp} library with the previously developed
sensor concepts.

\begin{longtable}[]{@{}llll@{}}
\caption{Build sensors with different capabilities
\label{Build_sensors_with_different_capabilities.csv}}\tabularnewline
\toprule
& 1D (Chapter \ref{d-single-sensor}) & 1D: dual sensor & 3D: fullsphere
(Chapter \ref{d-fullsphere})\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D (Chapter \ref{d-single-sensor}) & 1D: dual sensor & 3D: fullsphere
(Chapter \ref{d-fullsphere})\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30 & Cubic 30x30x30 & Cubic
20x20x20\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

These cover all the required functions described in the
Usecases\ref{usecases}. The biggest distinguishing feature, apart from
the sensor used, is the \passthrough{\lstinline!scan mode!}. In this
context, this describes whether the sensor can measure a
\passthrough{\lstinline!static!} fixed point on the magnet or if the
sensor can move \passthrough{\lstinline!dynamically!} around the magnet
using a controllable manipulator.

In the following, the hardware structure of a
\passthrough{\lstinline!static!} and \passthrough{\lstinline!dynamic!}
sensor is described. For the \passthrough{\lstinline!static!} sensor,
only the \passthrough{\lstinline!1D!} variant is shown, as this does not
differ significantly from the structure of the
\passthrough{\lstinline!1D: dual sensor!}, except it uses two
\passthrough{\lstinline!TLV493D!} sensors, mounted above and on top of
the magnet.

@@

The \passthrough{\lstinline!1D!}
sensor\ref{1D_sensor_contrsuction_with_universal_magnet_mount.png} is
the simplest possible sensor that is compatible with the
\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} platform
and also with the \gls{mrp}-library\ref{software-readout-framework}.

The electrical level here is based on a
\passthrough{\lstinline!Raspberry-Pi Pico!} together with the
\passthrough{\lstinline!MMC5603NJ!} magnetic sensor. The mechanical
setup consists of four 3D-printed components, which are fixed together
with nylon screws to minimise possible influences on the measurement.

Since the \passthrough{\lstinline!MMC5603NJ!} only has very limited
measuring range, even small neodymium magnets already saturate this
range, it is possible to use 3D-printed spacers above the sensor.

The standard magnet holder can be adapted for different magnet shapes
and can be placed on the spacer without play in order to be able to
perform a repeatable measurement without introducing measurement
irregularities by mechanically changing the magnet.

\hypertarget{d-fullsphere}{%
\subsection{3D: Fullsphere}\label{d-fullsphere}}

@@

The
\passthrough{\lstinline!3D Fullsphere!}\ref{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
sensor offers the possibility to create a 3D
map\ref{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
of the magnets. The magnet sensor is mounted on a movable arm, which can
move 180 degrees around the magnet on one axis. In order to be able to
map the full sphere, the magnet is mounted on a turntable. This permits
the manipulator to move a polar coordinate system.

\begin{figure}
\centering
\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
\caption{3D plot of an N45 12x12x12 magnet using the 3D fullsphere
sensor
\label{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}}
\end{figure}

As the magnets in the motors, as with the screws used in the 1D sensor,
can influence the measurements of the magnetic field sensor, the
distance between these components and the sensor or magnets was
increased. The turntable and its drive motor are connected to each other
via a belt.

On the electrical side, it also consists of a
\passthrough{\lstinline!SKR Pico!} stepper motor controller, together
with the \passthrough{\lstinline!TLV493D!} magnetic field sensor. This
was chosen because of its larger measuring range and can therefore be
used more universally without having to change the sensor of the arm.

\hypertarget{integration-of-an-industry-teslameter}{%
\subsection{Integration of an industry
Teslameter}\label{integration-of-an-industry-teslameter}}

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. This is shown here using a
temperature-compensated \passthrough{\lstinline!Voltcraft GM-70!}
telsameter\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png},
which has a measuring range of \passthrough{\lstinline!0-3T!} with a
resolution of 0.1mT. This offers an \passthrough{\lstinline!RS232!}
interface with a documented protocol for connection to a \gls{pc}. This
connectivity makes it possible to make the device compatible with the
\gls{mrp} library using interface software \cite{VoltcraftGM70Rest}
executable on the host \gls{pc}. However, it does not offer the range of
functions that the
\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} offers.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}
\caption{Voltcraft GM70 teslameter with custom \gls{pc} interface board
\label{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png}}
\end{figure}

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an \passthrough{\lstinline!RS232!} interface. As with the other
sensors, this interface consists of your
\passthrough{\lstinline!RaspberryPi Pico!} with an additional level
shifter. The Teslameter is connected to the microcontroller using two
free \gls{gpio}s in \gls{uart} mode. The
\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} was
adapted using a separate build configuration and the protocol of the
measuring device was implemented.

This software or hardware integration can be carried out on any other
measuring device with a suitable communication interface and a known
protocol thanks to the modular design.

@@

At the current state of implementation, it is only possible to detect
and use sensors that are directly connected to the \gls{pc} with the
\gls{mrp}-library. This has the disadvantage that there must always be a
physical connection. This can make it difficult to install multiple
sensors in measurement setups where space or cable routing options are
limited. To make sensors connected to a small
\passthrough{\lstinline!remote!} \gls{pc} available on the network, the
\passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
been developed. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
footprint and low power consumption make it a good choice. It can also
be used in a temperature chamber. The approach of implementing this via
a \gls{rest} interface also offers the advantage that several
measurements or experiments can be recorded at the same time with the
sensors.

@@

If time-critical synchronisation is required, \gls{ptp} and \gls{pps}
output functionality can be used on many \gls{sbc}, such as the
\passthrough{\lstinline!Raspberry-Pi Compute Module 4!}.
